Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2021-09-14 RR_manuscript/Draft_RR.Rmd
include reference to recruitment form and analytical approach questionnaire, includes temp. links

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient. Given the exploratory nature of our study, however, we will sample as many analysts as possible. We have received initial expression of interest to participate from more than 200 analysts.

>>>>

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
Social media advertising will be accompanied by a short recruitment form available at LINK.^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Recruitment form.]
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Analytical approach form.]).
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient. Given the exploratory nature of our study, however, we will sample as many analysts as possible. We have received initial expression of interest to participate from more than 200 analysts.
